---
title: "R Packages"
output: 
  learnr::tutorial:
    css: "css/style.css"
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is an R package?

An R package is essentially a collection of R function definitions. They usually also include helpful information about each function, examples of how to use them and tests to make sure they work as they should.

### Structure of an R package

### Where are R packages? (GitHub and CRAN)

## Contributing to an R package

There are two main reasons you might want to contribute to an R package:
- To expand what it can do (e.g., by adding a new function)
- To address a problem/issue within the package

### Adding new functions

You may have an idea for a function that would fit in well with a package.
Perhaps you have written a function that you often use in conjunction with that package.

For example, if you use `create_age_groups()` from our {phsmethods} package, you might find that you often want to summarise a dataset by age group after those groups have been created. So you could write a function that does this, and propose that it be added to {phsmethods} for others to use.

To add a function to a package, you will usually have to 'fork' or add a branch to the package's repository on GitHub. Then you can make changes to the package's code safely, without worrying about disrupting the package until you are finished making your changes.

Once you have done this you can create a new file in the folder named "R", where the R functions associated with a package are stored. The file should be named something like function-name.R, where you substitute "function-name" for the actual function name. Our new function for {phsmethods} will be called `mean_by_age()` so we will create a new file in the 'R' folder called 'mean_by_age.R'

Inside that file, we will write the code that defines our function. In this case, we will make a function that takes a dataframe, the name of the column containing age groups and the name of the column we want to summarise.

```{r}
mean_by_age <- function(data, age_col, summary_col) {
  data %>% group_by(across(age_col)) %>% 
    summarise(
      mean_age = mean(.data[[summary_col]])
    )
}
```

### Correcting/improving existing functions

### Publishing your contributions

## Creating an R package

### Writing functions

### Writing documentation

### Writing tests

### Publishing the package

## Resources
